% use ptex2pdf
\documentclass[11pt]{article}
\usepackage[sectionbib,numbers]{natbib}
\usepackage{fancyhdr}
\usepackage{url}
%\usepackage[colorlinks=true,linkcolor=blue,filecolor=blue,urlcolor=blue,dvipdfmx]{hyperref}
\usepackage[colorlinks=true,linkcolor=blue,filecolor=blue,urlcolor=blue,dvipdfmx]{hyperref}
\usepackage[top=30truemm,bottom=30truemm,left=25truemm,right=25truemm]{geometry}

\pagestyle{fancy}
\fancyhf{}
\rhead{\thepage}
\lhead{PFS Commissioning Workflow}
\rfoot{}

\usepackage[dvipdfmx]{graphicx}
\usepackage{amsmath,amssymb}
\usepackage[usenames]{color}
\usepackage{ascmac,fancybox}
% bounding box
\usepackage{mediabb}

% package for vector
\usepackage{bm}
% package for long table and coloured table
\usepackage{longtable}
\usepackage{lscape}
\usepackage{colortbl}
%caption package
\usepackage{caption}
\captionsetup[longtable]{width=0.90\textwidth}
\captionsetup[table]{width=0.90\textwidth}
\captionsetup[figure]{width=0.90\textwidth}

%spreadsheet table
%\usepackage{spreadtab}

%coloured text
\newcommand{\redtext}[1]{\textcolor{BrickRed}{#1}}
\newcommand{\grntext}[1]{\textcolor{OliveGreen}{#1}}
\newcommand{\orntext}[1]{\textcolor{Orange}{#1}}
\newcommand{\bluetext}[1]{\textcolor{BlueViolet}{#1}}
\newcommand{\suctitle}[1]{\textcolor{RoyalBlue}{{\large \bf #1}}}
\newcommand{\milestone}[1]{\textcolor{BlueGreen}{{\bf --- #1 ---}}}

% math units
\newcommand{\degree}{^\circ}

% path for figures
\graphicspath{{./figs/}}

% *** a dictionary           *** %
%  * process: work-flow process e.g. P-1, A-3
%  * sequence: sub-process in a given process. e.g. P-6 (AG function) consists of 3 sequences (focusing, pixel scale, guiding)
%  * step: working step of each process and/or sequence
% *** a dictionary (End) *** %

\title{PFS Commissioning Work Flow \\
\large{Reference ID: PFS-GEN-IPM004000-01 }}
\author{Yuki Moritani, Kiyoto Yabe, Naoyuki Tamura, and Atsushi Shimono \\
(PFS Project Office, Kavli IPMU)}
\date{
Issue 01, ver. 9: \today }
%\date{\today \\ ver. 1 September 2, 2015}

\begin{document}
%title and index
\maketitle
\tableofcontents

% Section: Overview
\section{Overview}
\input{overview}

% Section: Details of Procedure
\section{Details of Work Flow}

% MCS part
\renewcommand{\thesubsubsection}{M-\;\arabic{subsubsection}}
\subsection{Validation of MCS}\label{sec:MCS}
\input{step_MCS/M-01}
\input{step_MCS/M-02}
\input{step_MCS/M-03}
\input{step_MCS/M-04}

% PFI part
\renewcommand{\thesubsubsection}{P-\;\arabic{subsubsection}}
\subsection{Validation of PFI}\label{sec:PFI}
MCS will be delivered to the Subaru telescope one year before PFI delivery.
Hence, working process for PFI validation are considered assuming that we can install MCS to the Cassegrain focus.
\input{step_PFI/P-01}
\input{step_PFI/P-02}
\input{step_PFI/P-03}
\input{step_PFI/P-04}
\input{step_PFI/P-05}
\input{step_PFI/P-06}
\input{step_PFI/P-07}
\input{step_PFI/P-08}
\input{step_PFI/P-09}
\input{step_PFI/P-10}
%\input{step_PFI/P-11}
%\input{step_PFI/P-12}
%\input{step_PFI/P-13}

% SpS part
\renewcommand{\thesubsubsection}{S-\;\arabic{subsubsection}}
\subsection{Validation of SpS}\label{sec:SpS}
\input{step_SpS/S-01}
\input{step_SpS/S-02}
%\input{step_SpS/S-03}

% FoCCos part
\renewcommand{\thesubsubsection}{F-\;\arabic{subsubsection}}
\subsection{Validation of FoCCos}\label{sec:FoCCoS}
\input{step_CAB/F-01}
\input{step_CAB/F-02}

% All part
\renewcommand{\thesubsubsection}{A-\;\arabic{subsubsection}}
\subsection{Commissioning of All Systems}\label{sec:All}
%-- replaced to each other: 25 Apr. 2016 : start
\input{step_All/A-02}
\input{step_All/A-01}
%-- replaced to each other: 25 Apr. 2016 : end
%\input{step_All/A-03}
\input{step_All/A-04}
\input{step_All/A-05}
\input{step_All/A-06}
\input{step_All/A-07}

\input{details_tools}
\clearpage

% Raster Fields
\input{starcatalog.tex}

\clearpage

% Coordinates systems
%\input{coordinates.tex}

\clearpage

%Appendix
\appendix
%\renewcommand{\thesection}{Appendix \Alph{section}.}
\input{appendix.tex}
\input{abbreviation.tex}

\section*{Change log.}
\begin{itemize}
\item ver. 1: 7 October, 2015 \\
--- Released for informal meeting in Princeton.
\item ver. 2:  March 15, 2016
\item ver. 3: 10 May, 2016
--- Released for discussion with Subaru
\item ver. 4: 5 October, 2016 \\
--- Updates from informal meeting, and software collaboration meeting.
\item ver. 5: 7 January, 2017 \\
--- Update schedules of runs following the latest to-level schedule (as of Dec. 2016)
\item ver. 6: 1 May, 2018 \\
--- Update schedules of runs following discussion with Subaru in Jan. 2017., and the latest top-level schedule \\
--- Update following suggestion by J. Gunn in May 2017.
\item ver. 7: December 2019 \\
--- Change document structure \\
--- Update schedules based on project schedule as of 2019 July.
\item ver. 8: 11 February 2020 \\
--- Update process following the results of the Runs 0--2.
\item ver. 9: 11 June 2021 \\
--- Update process and schedule following allocated time in S21B.
\end{itemize}

\end{document}
