%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Check of Basic Functions of MCS on the Telescope [Daytime]}\label{secflow:MCSon}

\milestone{MCS is operated on the telescope for the first time.}

After installation to the telescope, basic functions of MCS are checked again, but on-telescope condition in this process.
During installing operation, the power of MCS will be kept on (TBC\footnote{Having UPS, MCS computer can be kept on. Still, the network will be disconnected}), so we should turn on the MCS electric devices (or reconnect to the network) again.

Then we check the following functions (the same as \ref{secflow:MCSoff}):

\begin{itemize}
\item MCS can read CMOS sensor with expected performance.
	\begin{itemize}
	\item dark level: No detectable dark current at 20--25 [decC] in one 0.8s frame
	\item noise level: $6.4 e^-$
	\item background level: \redtext{how much??}
	\item shutter: We take several images opening and closing the mechanical shutter to confirm it works properly.
	\end{itemize}
These values are cited from the CDR slides ({\tt MCS camera system.pdf}).
\item MCS can read environmental sensors.
	\begin{itemize}
	\item 7 temperature sensors on optics, mechanical structure, coolant lines, MCBox and electrical rack \redtext{(where exactly?)}
	\item flow meter
	\item microphone
	\end{itemize}
\end{itemize}

After the basic functions are confirmed to work, the calibration data (flat, bias and, dark?:TBC) of CMOS sensor shall be obtained, if they are not taken in the step of \ref{secflow:MCSoff}.
The stability of calibration data can be examined using the data in multiple runs.

\paragraph{Designated Tool for This Process}
We will prepare commands to check MCS functions, the same as \ref{secflow:MCSoff}.

%By sending command from gen2, we will also confirm communication between MCS and Gen2.

%\redtext{
%According to the MCS delta-CDR, the flat screen is attached MCS flange for obtaining flat-fielding, and 3--4 LEDs are attached near MCS-M1 module.
%On the other hand, because the Cassegrain stand-by flange has a space for light source on the top, the calibration data can be obtained during stand-by (TBD).
%}

\begin{itembox}[l]{\suctitle{Success Criteria}}
All MCS basic functions are verified --- power, CMOS sensor, telemetry.  \\
The calibration data (bias, flat, and dark?) of CMOS are acquired.

\bluetext{Required long time to analyze the data?: No. \\
--- We can check the functions in real-time}
\end{itembox}

