%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Validation of the Basic function of SCR and SpS [Daytime]}\label{secflow:SCR}

SpS modules (SM1, 2, 3,and 4) are operated in the designated room called SCR (Spectrgraph Clean Room) on the IR4 floor, where the temperature is controlled from 3 degC to 5 degC.
The Camera Assemblies are cooled down in the cryostat.
On the below floor (IR3), the compressors will be used during the operations.
Under such a condition, the following functions of SpS assemblies as well as SCR functions should be verified:
%We  also check the functions of SCR in this sequence.
\begin{itemize}
\item The temperature in SCR can be controlled stably in the range from 3 degC to 5 degC.
\item All SMs can switch Medium-Resolution mode and Low-Resolution mode (red arm).
\item All SMs can open and close blue and red shutters.
\item All SMs can move all other mechanical part. \redtext{Name}
\item All SMs can back-illuminate the fibers (by looking from GANG connectors of cable A?)
\item All SMs can read telemetry sensors
\item All SMs can read their all detectors within expected noise -- dark, bias.
\item The spots are on-focus in the detector.
\item We check the image quality and stability at a certain temperature and vibration [cf. Validation Roadmap by LAM: tests stability (2.5.8)].
Repeat temperature cycle and check repeatability.
The image quality is defined in the requirements {\tt REQ-SpS-47 (Test)}, which declares that the Ensquared Energy in more than 90\% detector area should be (1) 50\% within 3 x 3 pixels, and (2) 90\% within 5 x 5 pixels.
\item We demonstrate power failure mode
\item The exposure sequence works.
\end{itemize}

% We take Arc-lamp image through dummy cable B, and check focus of the spots on CCDs/detector by comparing spot size with reported by LAM.
% If the spots doesn't satisfy image quality, adjust assembly following partners' documents (and/or consulting them).
% We check the stability of the focus position in the operational range of the temperature.

\paragraph{Designated Tool for This Process}
We will prepare commands to check SpS functions.
This might be used as health check of the subsystems (TBD).

%Cool SCR and cryostats into operation temperature and check basic functions of SpS assemblies under the low temperature:

\begin{itembox}[l]{\suctitle{Success Criteria}}
All basic function of SCR and SpS is verified.
\end{itembox}