%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Check focal plane shift/tilt [Night-time]}\label{secflow:WFCTiltShift}

To have good image quality on the focal plane, WFC (and hence the instrument) need to be aligned in x/y/z and tilt with respect to the telescope primary mirror.
The misalignment of WFC with the primary mirror in x/y causes coma aberration across the field.
That in z defocuses images.
A tilt error induces coma aberration and focal plane tilt.
So it is important to minimize these errors to keep good image quality during observation. 
This alignment is carried out by Hexapod on POpt2 that can adjust the x/y/z and tilt of the assembly of WFC and PFI (see section \ref{sec:Hexapod}).


We slew the telescope to bright stars again, but defocused.
Using defocused ($\Delta$D5=0.5mm) image of AGCs, measure shift/tilt of WFC with respect to M1 and correct them.
The goal of correction is that shift is less than 0.5mm, and that tilt is less than 1 arcmin, with which the spot size (RMS) is less than 15 um.
[See Yoko Tanaka's report detailed procedure (WFC\_position.pdf: Japanese)]

To measure tilt and shift of WFC, 6 defocused image are needed on every AG camera.
As we use bright stars, we acquire such image by rotating the instrument.
Assuming it takes about 3min including positioning, one iteration needs about 20 min.
According to Yoko Tanaka's study, four iterations on average are needed to alignment.
Therefore, it takes ~80min for one position.

The parameters of Hexapod for alignment is registered as a function or table with respect to the elevation.
Therefore, we measure the Hexapd parameters at several elevations.
Given we measure them 5 positions (e.g., EL=30, 40, 50, 60, 75) and repeat three times at each elevation, 800 minutes, or 20 hours are needed for the correction.


\begin{itembox}[l]{\suctitle{Success Criteria}}
The focus is measured with the accuracy of $\sim$10 um \\
Misalignment of  WFC and M1 is corrected (shift: 0.5mm and tilt 1 arcmin)

Hexapod position at several elevation are measured and registered as correction parameters.

\bluetext{Required long time to analyze the data?: No. \\
--- We shall analyze the data in real-time to align WFC.
}
\end{itembox}