%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Telescope Pointing Analysis [Night-time]}\label{secflow:TPA1}

\milestone{PFS send Az/El offset measured using AGC to the telescope for the first time.}

Although there are originally 1-, 5-, 32-points Telescope Pointing Analysis (TPA) functions on the Subaru telescope, PFS can execute only 1- TPA.
Here, the number shows the numbers of stars to be observed at a given field.
PFS uses the same mount correction coefficients as HSC, and they are updated when HSC executed TPA.
(Operator can decide whether to update for PFS.)

By executing 1- TPA, offset angles for Az/EL are estimated.
These offset are used the additional parameters for mount correction coefficients for PFS.

For 1- TPA, the telescope control system drives the sequence as below:
\begin{enumerate}
\item Slew the telescope to set a certain star on the one of the AG camera.
%\item Take its image on the center camera.
%PFI has a small CMOS sensor ($\sim 9" \times 9"$) in the center of the FoV.
%The FoV of the center camera is large enough to acquire a bright star in the FoV even before TPA.
\item Take its image by AG camera.
\item Measure the Az/El offset, by measuring offset of the star from where it should be.
\item repeat [1-3] for different stars.
We will visit every 30 degree in the azimuth direction and every 15 degree in elevation from 30 -- 75 degree.
In total , Az/El offsets are  measured at 12 $\times$ 4 $=$ 48 field of view.
\item Average offset measured at sequence [3].
Update Az/El offset value of mount correction efficients, as the additional parameter.
\end{enumerate}

Assuming it will tale 900sec to obtain the data in a given field, 12 hours (900 $\times$ 48 seconds) are required.

\redtext{How much does the difference of the scale b/w FoV center and edge effect??}
%The offset derived from this process can be considered from the next telescope pointing. 

%In this step, we start with 1-, 5- TPA.
%The stars are chosen from various areas of sky so that the offset can be characterized as functions of telescope azimuth and elevation.
%Since PFI does not have any camera at the field center\footnote{There are discussion whether we locate a $\sim$ 1mm camera in the center of FoV, instead of fiducial fiber.}, a special care will be necessary to slew the telescope and calculate the offset.
%That is, we should slew telescope w/ offset ($\Delta \alpha$, $\Delta \delta$) in order to have image on the center of AG cameras.
%These offset is derived from $0^\mathrm{th}$-pass distortion map in the first operation (see below), but derived from updated distortion map after commissioning.

%After TPA, we check tracking error of the telescope.

\begin{itembox}[l]{\suctitle{Success Criteria}}
Obtain Az/El offset value of mount correction efficients.

\bluetext{Required long time to analyze the data?: No. \\
--- We shall analyze the data in real-time.
}
\end{itembox}